--- 
title: Truck Report
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Khoury
abstract: |
  This is a project describing the comptuation of truck reports.
output: rticles::acm_article
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(rticles)
library(dplyr)
library(readr)
```



```{r, message=FALSE, warning=FALSE, echo=FALSE}

file_regex <- ".scala$|\\.swift$|\\.go$|\\.js$|\\.cpp$|\\.h$|
\\.java$|\\.c$|\\.flow$|\\.php$|\\.rb$|\\.ts$|
\\.CC$|\\.cxx$|\\.groovy$|\\.sql$|\\.py$"

compute_truck_factor <- function(combined) {
  
  by_file_author <- combined %>% group_by(file, author.name) %>% summarise(
    all_added_lines = sum(added.lines)
  )
  
  by_file_author <- by_file_author %>% group_by(file) %>% summarise(
    max_lines_added = max(all_added_lines),
    owner = author.name[which(all_added_lines == max_lines_added)][1]
  )
  
  by_file_author <- by_file_author %>% group_by(owner) %>% summarise(
    num_files_owned = n()
  )
  
  owner_counts <- by_file_author[order(-by_file_author$num_files_owned),]$num_files_owned
  
  total_file_count <- sum(owner_counts)
  for (i in 1:length(owner_counts)) {
    if ((sum(owner_counts[1:i]) / total_file_count) > 0.5) {
      return(i)
    }
  }
}

```



```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
project_names <- c()
truck_factors <- c()
num_commits <- c()
num_files <- c()
num_authors <- c()


project_count <- 0

for (filename in list.files("./commit_metadata/")) {
  if (project_count %% 50 == 0) {
    print(project_count)
  }
  meta <- read.csv(paste("commit_metadata/", filename, sep = ""))
  file <- read.csv(paste("commit_files/",filename, sep = ""))
  combined <- inner_join(meta, file, by="hash") 
  if(nrow(file) != nrow(combined)) next
  combined <- subset(combined, grepl(file_regex, file))
  commits <- unique(combined$hash)
  files <- unique(combined$file)
  authors <- unique(combined$author.name)
  project_names <- append(project_names, filename)
  if (nrow(combined) == 0) {
      truck_factors <- append(truck_factors, 0)
  }
  else{
      truck_factors <- append(truck_factors, compute_truck_factor(combined))
  }
  
  num_commits <- append(num_commits, length(commits))
  num_files <- append(num_files, length(files))
  num_authors <- append(num_authors, length(authors))
  
  project_count <- project_count + 1
}

```



```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

results_df <- data.frame(project_name = project_names, num_authors=num_authors, num_files=num_files, num_commits=num_commits, truck_factor=truck_factors)

results_df <- results_df[(results_df$num_authors > 10),]

```


`r length(commits)` commits, `r length(files)` unique files and `r length(authors)` unique authors. I filtered the file types the same way Professor Vitek did in his report, keeping only files from known programming languages.

I only considered projects with more than 10 authors.

`r 100 * nrow(results_df[results_df$truck_factor == 1,]) / nrow(results_df)`% of projects have tf 1  
`r 100 * nrow(results_df[results_df$truck_factor == 2,]) / nrow(results_df)`% of projects have tf 2  
`r 100 * nrow(results_df[results_df$truck_factor == 3,]) / nrow(results_df)`% of projects have tf 3

```{r, message=FALSE, warning=FALSE, echo=FALSE}


plot(ecdf(results_df$truck_factor), xlab="Truck Factor", verticals=TRUE, do.points=FALSE, col.01line = NULL, xlim=c(1,10))


```



